Verifying Demonstrations

### 2018-11-01 paper/privacy-properties.tex
Comments on statements on receipt freeness

Coercion resistance is not possible to achieve for protests.
For instance, someone could simply physically bring Alice to a protest against her will.
Receipt freeness, while appealing at first glance, is not desirable in our context, as in contrast to voting, receipt freeness for \emph{how} the voter voted (\ie the cause of the protest) implies receipt freeness for \emph{that} the voter voted (\ie the protester was there) which conflicts with verifiability.

>>>>

Coercion resistance is not possible to achieve for protests.
For instance, someone could simply physically bring Alice to a protest against her will.
Receipt freeness, while appealing at first glance, is not desirable in our context, as in contrast to voting, receipt freeness for \emph{how} the voter voted (\ie the cause of the protest) implies receipt freeness for \emph{that} the voter voted (\ie the protester was there) which conflicts with verifiability.
\daniel{%
  No, that implication is not true, counter example:
  There is receipt freeness for how a elector voted, but not that they voted.
  As Simon pointed out, they tick me off, so it's visible that I've voted.
  But no one will ever know for which party I voted.%
}

\daniel{%
  This doesn't conflict with verifiability either.
  I keep track of the ballot box, as long as that and all ballots inside are 
  treated properly, I know my ballot is safe and counted.%
}

\daniel{%
  In our case:
  I have a key issued on a smartcard and it's tied to my identity.
  If the hardware corrupts itself after issuing the \ac{NIZK} proof, then there 
  is no way to check whether I created \(\pid = \ACprf[_k][\cid]\) or \(\pid' = 
    \ACprf[_k][\cid']\).
  I could've downloaded both from the ledger.
  But I know which is mine, I can submit it, and as long as the block where it 
  was included is intact I know my proof-share is included as well --- even if 
  I forget what it looked like.%
}
